---
title: "Introduction to Colorify"
author: "Maurits Unkel"
date: "2024-06-16"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{introduction_to_my_package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(myPackage)

# https://r-package-guide.netlify.app/vignettes

# build vignette - test with: help(package = "colorify") & browseVignettes("colorify")
## keep in mind: devtools::install_github("mauritsunkel/colorify", build_vignettes = TRUE)

# consider doc site: https://r-package-guide.netlify.app/building-a-website-with-pkgdown
## check more in package building site from Hadley Wickham ^
```

\

# Introduction

This is an example vignette for the `myPackage` package, an example package created as part of my tutorial on making R packages. This practice package contains a couple of functions. One of them, `random_movie_recommendation`, utilizes the `ggplot2movies` package from CRAN, which provides a dataset of movies. The other function, `calculate_group_mean`, uses example data included in `myPackage`.

## Example Data

The `example_data` dataset included in this package contains a small sample of data for demonstration purposes. It has three columns: `ID`, `Age`, and `Likes_Coffee`. Here is how you can load and view the dataset:

```{r}
# Load the example dataset
data(example_data, package = "myPackage")

# View the dataset
example_data
```

\

# Random Movie Recommendation

The `random_movie_recommendation` function randomly selects and returns the title of a movie from the `ggplot2movies` dataset. This function is useful for getting a random movie suggestion.

Here is how you can use the `random_movie_recommendation` function:

```{r}
random_movie_recommendation()
```

\

# Calculate Group Mean

The `calculate_group_mean` function calculates the mean of a numeric variable for rows where a specified binary variable is TRUE. In our example dataset, it can be used to find the mean age of people who like coffee.

Here is how you can use the `calculate_group_mean` function:

```{r}
calculate_group_mean(example_data, "Age", "Likes_Coffee")
```